{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-19 Paper/main.tex
Moved Paper to own directory
Increment

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{figure}[H]\label{fourier_basis}
	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
	\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}

@@

	\begin{figure}[H]\label{bspline_basis}
		\includegraphics[width = \textwidth]{Graphics/Bspline_Basis.pdf}
		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
	\end{figure}

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$. Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

@@

	\subsection{Motivation}
	For the simulation study, we deviate from the standart simulation setting. Instead of generating data by ourself, we use the data from the gasoline dataset ($NIR$) to predict the octane ratings of gasoline samples, relying on the introduced methods. The dataset, which contains 60 i.i.d. observations with each 400 measurements, was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}).

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated similar curves from the gasoline dataset. This is motivated by the Karhunen-Loeve-Expansion {\color{green} link formula}
	 First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots. These smooth curves are then centred, before performing FPCA. For simplification, we assume that
	$\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j}\independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{Graphics/smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{Graphics/bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

@@

	\begin{figure}[H]\label{Wiener_plot}
		\includegraphics[width = \textwidth]{Graphics/Wiener_plot.pdf}
		\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
	\end{figure}

>>>>

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage[font=small,skip=2pt]{caption}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{figure}[H]\label{fourier_basis}
	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
	\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}

@@

	\begin{figure}[H]\label{bspline_basis}
		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
	\end{figure}

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$. Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

@@

	\subsection{Motivation}
	For the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate. The dataset, which contains 60 i.i.d. observations with 401 measurements, allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}). The optimal number L of basis functions were chosen for each model through 10-fold Cross-Validation. Additionally, even for FPCR, we discovered what number of components produces the best. As a result, we progressed the application with the derived outcomes.

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset. This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots. These smooth curves are then centered, before performing FPCA. It is supposed that each estimated score follows normal distribution with the assumption that the variance equals its eigenvalue. Finally, we obtain the generated curves

@@

		\begin{itemize}
			\item $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{../Graphics/smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{../Graphics/bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

@@

	\begin{figure}[H]\label{Wiener_plot}
		\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
		\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
	\end{figure}
